Stateless Model Checking with Data-Race Preemption Points

### 2016-07-15 oopsla-16/overview.tex
address the rest of reviewer D non-mandos

	{\bf Variants of Happens-Before.}
	Most prior work focuses on {\em Happens-Before} (HB) \cite{lamport-clocks,djit,fasttrack} as the order relation between accesses.
\cite{predictive-dr} and \cite{hybriddatarace} identify a problem with this approach:
it cannot identify access pairs separated by an unrelated lock operation which could race in an alternate interleaving,
as shown in the example program in Figure~\ref{fig:hb-example}(a).
We call such unreported access pairs {\em false negatives}.
\cite{hybriddatarace} introduces the {\em Limited HB} relation,
which will report such potential races
by considering only blocking operations like {\tt cond\_wait} to enforce the order.
However, consider the similar program in Figure~\ref{fig:hb-example}(b),
in which the access pair ceases to exist in the alternate interleaving.
Limited HB will report all potential races, avoiding false negatives \cite{tsan},
but at the cost of necessarily reporting some such {\em false positives}.

@@

Stand-alone data-race analyses must avoid inundating the user with false alarms \cite{racerx}.
%However,
This work incorporates data-race analysis in an internal feedback loop,
using model checking to automatically test each potential race
and report only directly observed failures to the user.
%Our convergence theorem requires identifying all potential data-races to provide total verification (\sect{\ref{sec:totalverif}})
%% TODO CAMREADY: cite our soundness proofs tech report in this paragraph as well
%Hence, we employ Limited HB in this paper},
%accepting some overhead from false positives for the sake of total verification (\sect{\ref{sec:totalverif}}).
\revisionx{Hence, we can accept some overhead from Limited HB's false positives for the sake of finding data-race candidates more quickly.
In \sect{\ref{sec:eval}} we will evaluate how HB and Limited HB each influence \quicksand's bug-finding and verification speed.
}

>>>>

	{\bf Variants of Happens-Before.}
	Most prior work focuses on {\em Happens-Before} (HB) \cite{lamport-clocks,djit,fasttrack} as the order relation between accesses.
\cite{predictive-dr} and \cite{hybriddatarace} identify a problem with this approach:
it cannot identify access pairs separated by an unrelated lock operation which could race in an alternate interleaving,
as shown in the example program in Figure~\ref{fig:hb-example}(a).
We call such unreported access pairs {\em false negatives}.
However, consider the similar program in Figure~\ref{fig:hb-example}(b),
in which the access pair ceases to exist in the alternate interleaving.
\cite{hybriddatarace} introduces the {\em Limited HB} relation,
which will report such potential races
by considering only blocking operations like {\tt cond\_wait} to enforce the order.
Limited HB will report all potential races, avoiding \revisionx{many} false negatives \cite{tsan},
but at the cost of necessarily reporting some such {\em false positives}.

@@

\revisionx{Being dynamic analyses, both HB and Limited HB may suffer false negatives when a racy access pair is not executed at all in a specific interleaving.
Limited HB offers the advantage of identifying a potential race as long as the access pair is observed under any interleaving,
rather than requiring the accesses to be adjacent in time, as HB would.}
While stand-alone data-race analyses must avoid inundating the user with false alarms \cite{racerx},
%However,
we incorporate data-race analysis in an internal feedback loop,
using model checking to automatically test each potential race
and report only directly observed failures to the user.
%Our convergence theorem requires identifying all potential data-races to provide total verification (\sect{\ref{sec:totalverif}})
%% TODO CAMREADY: cite our soundness proofs tech report in this paragraph as well
%Hence, we employ Limited HB in this paper},
%accepting some overhead from false positives for the sake of total verification (\sect{\ref{sec:totalverif}}).
\revisionx{Hence, we can accept some overhead from Limited HB's false positives for the sake of finding data-race candidates more quickly.
In \sect{\ref{sec:eval}} we will evaluate how HB and Limited HB each influence \quicksand's bug-finding and verification speed.
}
